---
title: "Session 2 practice"
author: "Eugina Leung"
date: "4 July 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Practice with layers (Task 0)
```{r}
library(ggplot2)
mpg
g <- ggplot(mpg, aes(x = displ, y = hwy))
g + geom_point(aes(colour = drv))
g + geom_point() + facet_wrap(~drv)
```
<br />
Practice with layers (Task 1)<br />
============================ <br />
*Create a plot with 1 layer: <br />
*x mapped to displ <br />
*y mapped to hwy <br />
*colour mapped to trans <br />
*geometry point <br />
*default stat and position for point <br />
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) +geom_point(aes(colour=trans))
ggplot(mpg, aes(x = displ, y = hwy, colour = trans)) +geom_point()
```
<br />
Practice with layers (Task 2)<br />
============================ <br />
*Defaults for all layers:<br />
*x →→ displ <br />
*y →→ hwy <br />
*Layer 1: <br />
*geom point <br />
*default stat and position<br />
*point colour is set to "red" <br/>
*Layer 2: <br/>
*geom smooth <br/>
*default stat and position<br/>
*no variables mapped to colour <br/>
```{r}
ggplot(mpg, aes(x=displ, y = hwy))+geom_point(aes(colour="red"))+geom_smooth()
```
<br />
Practice with layers (Task 3)<br />
============================ <br />
Defaults for all layers:<br />
x →→ displ<br />
y →→ hwy<br />
colour →→ drv<br />
Layer 1:<br />
geom point<br />
default stat and position<br />
Layer 2:<br />
geom smooth<br />
default stat and position<br />
pass in method='lm' to get linear (rather than LOESS) regression<br />
pass in se=FALSE to suppress confidence bands<br />
```{r}
ggplot(mpg,aes(x=displ, y=hwy, colour=drv))+geom_point()+geom_smooth(method="lm", se=FALSE)
```
<br />
Practice with layers (Task 4)<br />
============================ <br />
Defaults for all layers:<br />
x →→ displ<br />
y →→ hwy<br />
colour →→ cyl (as discrete values)<br />
Layer 1:<br />
geom point<br />
default stat and position<br />
Layer 2:<br />
geom smooth<br />
default stat and position<br />
```{r}
ggplot(mpg, aes(x=displ, y=hwy, colour=factor(cyl)))+geom_point()+geom_smooth()
```